---
title: "Data frames"
author: "Adrian Figueroa Rodriguez"
date: "7 de octubre de 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 6.1 What's a data frame?

You may rember form the chapter about matrices that all the elements that you put in a matrix shoud be of the same type. Back then, your data set on Star Wars only contained numeric elements.

When doing a market reasearch survey, however, you often have questions such as:
Are you maried? or yes/no questions (logical), How old are you? (numeric), What is your opinion on this product? or other open-ended questions (character),...

The output, namely the respondents answers to the questions formulated above, is a data set of different data types. You will often find yourself working with data sets that contoin different data types instead of only one.

A data frame has the variables of data set as colums and the observations as rows. This will be a familiar concept for those coming from different statistical software packages such as SAS or SPSS

```{r}
# Print out built-in R data frame
mtcars

class(mtcars)
```

### 6.2 Quick, have a look at your data set

```{r}
head(mtcars)
tail(mtcars)
```

### 6.3 Have a look at the structure

```{r}
str(mtcars)
```

### 6.4 Create a data frame

```{r}
# My try with: 
# Definition of vectors
name <- c("Mercury", "Venus", "Earth", "Mars", "Jupiter", "Saturn", "Uranus", "Neptune", "X")
name

# Type of vectors
type <- c("Terrestrial planet", "Terrestrial planet", "Terrestrial planet", "Terrestrial planet", "Gas giant", "Gas giant", "Gas giant", "Gas giant", "chimichangas")
type

# Diameter vector
diameter <- c(0.382, 0.949, 1, 0.532, 11.209, 9.449, 4.007, 3.883, 2.111)
diameter

# Rotation vector
rotation <- c(58.64, -243.02, 1, 1.03, 0.41, 0.43, -0.72, 0.67, 1.555)
rotation

# Rings Vector
rings <- c(FALSE, FALSE, FALSE, FALSE, TRUE, TRUE, TRUE, TRUE, FALSE)
rings

# Create a data frame from the vectors
planets_df <- data.frame(name, type, diameter, rotation, rings)
planets_df

class(planets_df)
```


### 6.5 Creating a data frame (2)

```{r}
# Check the structure of planets_df
str(planets_df)
```

### 6.6 Selection of data frame elements

```{r}
# The planets_df data frame from the previous exercise is pre-loaded

# Print out diameter of Mercury (row 1, column 3)
planets_df[1,3]

# Print out data for Mars (entire fourth row)
planets_df[4,]

# My try
dimond_vecotr <- planets_df[5:8, "diameter"]
lvls <- planets_df[5:8, "type"]
class(lvls)
str(lvls)
head(lvls)
```

### 6.7 Selection of data frame elements (2)

```{r}
# The planets_df data frame from the previous exercise is pre-loaded

# Select first 5 values of diameter column
planets_df[1:5, "diameter"]
```

### 6.8 Olny planets with rings

```{r}
# planets_df is pre-loaded in your workspace

# Select the rings variable from planets_df
rings_vector <- planets_df$rings

# Print out rings_vector
rings_vector

# My example
type_vector<- planets_df$type
type_vector

names_vector <- planets_df$type
names_vector
```

### 6.9 Only planets with rings(2)

```{r}
# planets_df and rings_vector are pre-loaded in your workspace
type_vector


# Adapt the code to select all columns for planets with rings
planets_df[rings_vector, FALSE]

# My try
planets_df[names_vector, "Gas giant"]
```

### 6.10 Only planets with rings but shorter

```{r}
# planets_df is pre-Loaded in your workspace 

# Select planets with diameter < 1
subset(planets_df, subset = diameter < 1)
```

### 6.11 Sorting

```{r}
# planets_df is a pre-Loaded in your workspace

# Use order() to create positions

positions <- order(planets_df$diameter)

# Use position to sort planets_df

planets_df[positions,]
```




















