---
title: "Factors"
author: "Adrian Figueroa Rodriguez"
date: "7 de octubre de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Factors

Very often, data falls into a limited number of catagories. For example, human hair color can be categorized as black/brown/blonde/red/grey/white (and perhaps a few more options for people who dye it). In R, categorical data is stored in factors. Given the importance of thse factors in data analysis, you should start learning how to create, subset and compare them now!!

### 5.1 What's factor and why would you use it?

```{r}
# Assign to the variable theory what this chapter is about!

theory <- "factors for categorical variables"
```

### 5.2 What's a factor and why would you use it? (2)

```{r}
# Sex vector
sex_vector <- c("Male", "Female", "Female", "Male", "Male")
sex_vector

# Convert sex_vector to a factor
factor_sex_vector <- factor(sex_vector)

# Print out factor_sex_vector
factor_sex_vector
```

### 5.3 What's a factor and why would you use it? (3)

```{r}
# Animals
animals_vector <- c("Elephant", "Giraffe", "Donkey", "Horse")
animals_vector

class(animals_vector)

factor_animals_vector <- factor(animals_vector)
factor_animals_vector

# Temperature
temperature_vector <- c("High", "Low", "High", "Low", "Medium")
temperature_vector
```

### 5.4 Factor levels

```{r}
# Code to build factor_survery_vector
survey_vector <- c("M", "F", "F", "M", "M")
survey_vector

factor_survey_vector <- factor(survey_vector)
factor_survey_vector

# Specify the levels of factor_survey_vector
levels(factor_survey_vector) <- c("Female", "Male")
factor_survey_vector
```

### 5.5 Summarizing a factor

```{r}
# Build factor_survey_vector with clean levels
survey_vector <- c("M", "F", "F", "M", "M")
survey_vector

factor_survey_vector <- factor(survey_vector)
levels(factor_survey_vector) <- c("Female", "Male")
factor_survey_vector

# Generate summary for survey_vector
summary(survey_vector)

# Generate summary for factor_survey_vector
summary(factor_survey_vector)
```

### 5.6 Battle of the sexes

```{r}
# Build factory_survey_vector with clean levels
survey_vector <- c("M", "F", "F", "M", "M")
factor_survey_vector <- c("Female", "Male")

# Male
male <- factor_survey_vector[1]
male

# Female
female <- factor_survey_vector[2]
female

# Battle of the sexes: Male 'larger'than female?

male > female
```

### 5.7 Ordered factors

```{r}
# Create speed_vector
speed_vector <- c("Medium", "Slow", "Slow", "Medium", "Fast")
```

### 5.8 Ordered factors (2)

```{r}
# Create speed_vector
speed_vector <- c("Medium", "Slow", "Slow", "Medium", "Fast")
speed_vector

# Add your code below
factor_speed_vector <- factor (speed_vector, ordered = TRUE, levels = c("Slow", "Medium", "Fast"))

# Print factor_speed_vector
factor_speed_vector

summary(factor_speed_vector)
```

### 5.9 Comparing ordered factors

```{r}
# Create factor_speed_vector
speed_vector <- c("Medium", "Slow", "Slow", "Medium", "Fast")
factor_speed_vector <- factor(speed_vector,ordered = TRUE, levels = c("Slow", "Medium", "Fast"))

# Factor value for second data analyst
da2 <- factor_speed_vector[2]
da2

# Factor value for fifth data analyst
da5 <- factor_speed_vector[5]
da5

# Is data analyst 2 fasta data analyst5?
da2 > da5
```
