---
title: "Matrices"
author: "Adrian Figueroa Rodriguez"
date: "6 de octubre de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapter 4 Matrices

In this chapter you will learn how to work with matrices in R. By the endo of the chapter, you will be able to create matrices and to understand how you can do basic computations with them. You will analyze the box office numbrers of Star Wars to illustrate the use of matrices in R. May the force be with you!

### 4.1 What's a matrix?

```{r}
# Construct a matrix with 3 rows that contain 1 up to 9
matrix(1:9, byrow = TRUE, nrow = 3)
```



### 4.2 Analyze matrices, you shall

```{r}
new_hope <- c(460.998, 314.4)
empire_strikes <- c(290.475, 247.900)
return_jedi <- c(309.306, 165.8)

# Create box_office
box_office <- c(new_hope, empire_strikes, return_jedi)
box_office

star_wars_matrix <- matrix(box_office,nrow = 3, byrow = TRUE)
star_wars_matrix
```

### 4.3 Naming a matrix

```{r}
# Box office Star Wars (in millions!)

new_hope <- c(460.998, 314.4)
empire_strikes <- c(290.475, 247.900)
return_jedi <- c(309.306, 165.8)

# Construct Matrix
star_wars_matrix <- matrix(c(new_hope, empire_strikes, return_jedi), nrow = 3, byrow = TRUE)

# Vectors region and title, used for naming
region <- c("US","Non-US")
titles <- c("A New Hope", "The Empire Strikes Back", "Return of the Jedi")

# Name the colums with region
colnames(star_wars_matrix) <- region

# Name the rows with titles
rownames(star_wars_matrix) <- titles

# Print out star_wars_matrix
star_wars_matrix
```
### 4.4 Calculating the worldwide box office

```{r}
# Construct star_wars_matrix
box_office <- c(460.9988, 314.4, 290.475, 247.00, 309.306, 165.8)
star_wars_matrix <- matrix(box_office, nrow = 3, byrow = TRUE,
                           dimnames = list(c("A New Hope", "The Empire Strikes Back", "Return of the Jedi"), c("US", "Non-US")))

# Calculate worldwide box office figures
worldwide_vector <- rowSums(star_wars_matrix)
worldwide_vector
```

### 4.5 Adding column for the Worldwide box office

```{r}
# Construct star_wars_matrix
box_office <- c(460.998, 314.4, 290.475, 247.900, 309.306, 165.8)
star_wars_matrix <- matrix(box_office, nrow = 3, byrow = TRUE,
                           dimnames = list(c("A New Hope", "The Empire Strikes Back", "Return of the Jedik"), c("US", "Non-US")))

# The worldwide box office figures
worldwide_vector <- rowSums(star_wars_matrix)

# Bind the new variable worldwide_vector as a colum of star_wars_matrix
all_wars_martrix <- cbind(star_wars_matrix, worldwide_vector)
all_wars_martrix
```

### 4.6 Adding a row

```{r}
# Construct star_wars_matrix
box_office <- c(460.998, 314.4, 290.475, 247.900, 309.306, 165.8)
star_wars_matrix <- matrix(box_office, nrow = 3, byrow = TRUE,
                           dimnames = list(c("A New Hope", "The Empire Strikes Back", "Return of the Jedi"), c("US", "Non-US")))

# Construct start_wars_matrix2
box_office2 <- c(474.5, 552.5, 310.7, 338.7, 380.3, 468.5)
star_wars_matrix2 <- matrix(box_office2, nrow = 3, byrow = TRUE,
                             dimnames = list(c("The Phantom Menace", "Attack of the Clone", "Revenge of the Sith"), c("US", "Non-US")))

# Combine both Star Wars trilogies in one matrix
all_wars_martrix <- rbind(star_wars_matrix, star_wars_matrix2)
all_wars_martrix
```

### 4.7 The total box office revenue for the entire saga

```{r}
# all_wars_matrix
all_wars_martrix

# Total revenue for US and Non-US
total_revenue_vector <- colSums(all_wars_martrix)

# Print out total_revenue_vector
total_revenue_vector
```

### 4.8 Selection of matrix elements


```{r}
# all_wars_matrix is available in your workspace
all_wars_martrix

# Select the Non-US revenue for all movies
non_us_all <- all_wars_martrix[,2]
non_us_all

# Average Non-US revenue
mean(non_us_all)

# Select the Non-US revenue for first two movies
non_us_all <- all_wars_martrix[1:2,2]
non_us_all

# Average Non-US revenue for first two movies
mean(non_us_all)
```

### 4.9 A little arithmetic with matrices

```{r}
# all_wars_matrix is available in your workspace
all_wars_martrix

# Estimate the visitors
visitors <- all_wars_martrix / 5

# Print the estamte to the console
visitors
```

### 4.10 A little arithmetic with matrices (2)

```{r}
# all_wars_matrix and ticket_prices_matrix are avalible in your workspace
all_wars_martrix

# Construct ticket_prices
ticket_office <- c(5,6,7,4,4.5,4.9)
ticket_prices1 <- matrix(ticket_office, nrow = 3, byrow = TRUE,
                        dimnames = list(c("A New Hope", "The Empire Strikes Back", "Return of the Jedi"), c("US", "Non-US")))


# Construct both Star Wars trilogies in one matrix
ticket_prices_matrix <- rbind(ticket_prices1, ticket_prices2)
ticket_prices_matrix

# Estimated number of visitors
visitors <- all_wars_martrix / ticket_prices_matrix

# US Visitors
us_visitors <- visitors[,1]
us_visitors

mean(us_visitors)
```