---
title: "Chapter 3 Vectors"
author: "Adrian Figueroa Rodriguez"
date: "4 de octubre de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown Vectors

In this free R course, we'll take you on a trip to Vegas, where you will lear how to analyze your gambiling results using vectors in R! After completing this chapter, you will be able to create vectors in R, name them, select elements from them and compare different vectors.

### 3.1 Crate a vector

```{r}
# Define the varialbe vegas
vegas <- "Go!"
```

### 3.2 Create a vector (2)

```{r}
# Complete the code for boolean_vector
boolean_vector <- c(TRUE, FALSE, TRUE)
```

### 3.3 Create a vector (3)
```{r}
poker_vector <- c(140,-50,20,-120,240)
roulette_vector <- c(-24,-50,100,-350,10)
```

### 3.4 Name a vector

```{r}
# Poker winnings form M to F
poker_vector <- c(140, -50, 20, -120, 240)

# Roulette winnings from M to F
roulette_vector <- c(-24,-50, 100, -350, 10)

# Assign days as names of poker vector
names(poker_vector) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

names(roulette_vector) <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

```

### 3.5 Naming a vector (2)


```{r}
# Poker winnings from M to F
poker_vector <- c(140,-50,20,-120,240)

# Roulette winnings from M to F
roulette_vector <- c(-24,-50,100,-350,10)

# The variable days_vector
days_vector <- c("Monday","Tuesday", "Wednesday","Thursday","Friday")

# Assign the names of the day to roulette_vector and poker_vector
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector
```

### 3.6 Calculating total winnings

```{r}
A_vector <- c(1,2,3)
B_vector <- c(4,5,6)

# Take the sum of A_vector and B_vector
total_vector <- A_vector + B_vector

# Print out total_vector
total_vector
```

### 3.7 Calculating total winnings (2)

```{r}
# Poker and roulette winnings from M to F
poker_vector <- c(140, -50, 20, -120, 240)

roulette_vector <- c(-24, -50, 100, -350, 10)

days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Assign to total_daily how much you won/lost on each day

total_daily <- poker_vector + roulette_vector
total_daily
```

### 3.8 Calculating total winnings (3)

```{r}
# Poker and roulette winnings from M to F
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Total winnings with poker
total_poker <- sum(poker_vector)
total_poker

# Total winnings with roulette
total_roulette <- sum(roulette_vector)
total_roulette

# Total winnings overall
total_week <- total_roulette + total_poker
total_week

# Print out total_week
total_week
```

### 3.9 Comparing total winnings


```{r}
# Poker and roulette winnings from M to F
poker_vector <- c(140,-50,20,-120,240)
roulette_vector <- c(-24,-50,100,-350,10)
days_vector <- c("Monday","Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Calculate total gains for poker and roulette
total_poker <- sum(poker_vector)
total_poker
total_roulette <- sum(roulette_vector)
total_roulette
total_winings <- total_poker + total_roulette
total_winings

# Check if you realized higher total gains in poker than in roulette
total_poker > total_roulette
```

### 3.10 Vector selection: the good times

```{r}
# Poker and roulette winnings from M to F
poker_vector <- c(140,-50,20,-120,240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")

names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
poker_wednesday <- poker_vector[3]
poker_wednesday
```

### 3.11 Vector selection: the good times (2)



```{r}
# Poker and roulette winnings from M to F
poker_vector <- c(140,-50,20,-120,240)
roulette_vector <- c(-24,-50,100,-350,10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
poker_midweek <- poker_vector[c(2,3,4)]
poker_midweek
```

### 3.12 Vector selection: the good times (3)

```{r}
# Poker and roulette winnings from M to F
poker_vector <- c(140,-50,20,-120,240)
roulette_vector <- c(-24,-50,100,-350,10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Define a new variable based on a selection
roulette_vector <- roulette_vector[2:5]
roulette_vector
```

### 3.13 Vector selection: the good times (4)

```{r}
# Poker and roulette from M to F
poker_vector <- c(140,-50,20,-120,240)
roulette_vector <- c(-24,-50,100,-350,10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Select poker results for M, T & W
poker_start <- poker_vector[c("Monday", "Tuesday", "Wednesday")]
poker_start

# Calculate the averages of the elements in poker_start
mean(poker_start)
```


### 3.14 Selection by comparision - Step 1
```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make mone yon poker?
selection_vector <- poker_vector >0

# Print out slection vector
selection_vector
```

### 3.15 Selection by comparision - Step 2

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on poker?

selection_vector <- poker_vector >0
selection_vector

# Select from poker_vector these days
poker_winning_days <- poker_vector[selection_vector]
poker_winning_days
```


### 3.16 Advances selection

```{r}
# Poker and roulette winnings from Monday to Friday:
poker_vector <- c(140, -50, 20, -120, 240)
roulette_vector <- c(-24, -50, 100, -350, 10)
days_vector <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday")
names(poker_vector) <- days_vector
names(roulette_vector) <- days_vector

# Which days did you make money on roulette?
selection_vector <- roulette_vector > 0
selection_vector

# Select from roulette_vector these days
roulette_winning_days <- roulette_vector[selection_vector]
roulette_winning_days
```